---
title: "case_study"
author: "Mengfan Luo"
date: "23/10/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Load dataset

```{r}
data("nyc_airbnb")
```







```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(borough = neighbourhood_group)
```

# Let's count

```{r}
nyc_airbnb %>% 
  janitor::tabyl(borough,room_type)
  
nyc_airbnb %>% 
  count(borough,room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```



* How many rentals are there? Of what type? In what places?

* Is price correlated with review scores?

* Which neighborhood is most popular?

* Which neighborhood has the highest review?

* Is availability related to peice?

* Is room type related to neighborhood?

* Is length of state related to neighborhood group?



## My question: IS minimum_nights related to room_type?


```
nyc_airbnb %>% 
  ggplot(aes(x = minimum_nights))+
  geom_histogram()
  ggplot(aes(x = minimum_nights,y = price,color = room_type))+
  geom_point(size = 5, alpha = .6)
```

Price and room type


```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price))+
  geom_point()+
  facet_grid(.~room_type)
```

Price and neighbourhood?

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price,na.rm = TRUE)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan",
         price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood,price)) %>% 
  ggplot(aes(x = neighbourhood, y = price))+
  geom_boxplot()+
  coord_flip()+
  facet_grid(.~room_type)

```

Price vs location

```{r}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(5000) %>% ##deal with large datasets
  ggplot(aes(x = lat, y = long,color = price))+
           geom_point(alpha = .5)
```


## retry leaflet

```{r, eval = FALSE}
nyc_airbnb %>% 
  
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~lat,~long)



```




















